Discrete Ordinates

### 2017-06-12 docprep/chapbib.tex
Updates

\section{CT Dose Estimation}
As discussed in Chapter 1, the dose a patient receives from both diagnostic CT procedures and radiation therapy is of great concern to the medical community [CITE]. However, dose quantification is not currently patient specific. Measuring the dose in a patient directly is impossible, intead the air kerma (measured in Gy), which measures the x-ray beam intensity, and can be measured directly [CITE]. As the x-ray beam passes through the patient, it deposits energy. The energy deposition per unit mass is the absorbed dose (measured in Gy) which is then weighted by the radiation type to give the equivalent dose (measured in Sv). The equivalent dose quantifies the biological detriment to the patient from the procedure. The effective dose (measured in Sv) accounts for the radiosensitivity of each organ and is the most meaningful measure of risk to the patient. Any two procedures that result in the same effective dose to the patient carry the same acute and long-term risks. Any procedure that gives an effective dose to a patient has the same risk as any procedure that would give the same whole body dose.

@@

Monte Carlo codes such as TOPAS [CITE], Geant4 \citep{ref:agostinellis}, and MCNP6 [CITE] are the current gold standard in computational dosimetry \citep{ref:jiax}. This work compares results to those obtained from MCNP6. MCNP6 is a Monte Carlo code developed for general purpose particle transport and is well validated. MCNP6 was selected for comparison because it is so well validated and the input files can be easily generated procedurally. Codes whose input such as Geant4 do not lend themselves easily to procedural code generation are difficult to benchmark precisely against for arbitrary computational phantoms.

@@

The method of characteristics solves the characteristic form of the Boltzmann transport equation which is defined along a single direction (called the characteristic). Along that direction, the 3-dimensional gradient operator found in the full Boltzmann equation (see Sec.~\ref{sec:lbe}) becomes a 1-dimensional derivitive. This reduction gives rise to an analytical solution along the characteristic [CITE]. Sufficient characteristic solutions solved simulateously gives the solution over the entire problem domain. Currently, though, MOC has not been extended to full 3D, instead, hybrid methods such as the NEM-$S_N$ technique employed by DeCART have been used. DeCART uses 2D MOC to solve planar slices of reactor transport problems and links the slices using diffusion~\citep{ref:hursinm}. Another MOC implementation is the TRANSMED code which was used to compute external beam therapy dose profiles accurately~\citep{ref:williamsm}. Method of characteristic solutions have been extended to the time dependent domain by \citet{ref:hoffmana}.

@@

Fundamentally, all reconstructions algorithms are based on a thin parallel beam of x-rays rotating axially about a patient to produce a sinogram. The inverse radon transform backprojects each row of the sinogram back to physical space. Filtering each row in Fourier space and then compositing all layers together recreates the image [CTIE]. This methodology has been extended to fan beams [CITE] and cone beams [CITE]. Besides the filtered backprojection (FBP) method, iterative reconstruction techniques can also be applied to greatly improve the image reconstruction quality [CITE].

@@

Along any particular ray, monoenergetic particles will attenuate through a homogenous media according to the Beer-Lambert law given in Eq.~\ref{eq:beer_lambert} [CITE] resulting in a small fraction of the source particles reaching the detector. This phenomena leads to an image of the attenuating media but also results in the detector receiving information about the attenuation coefficient, $\mu$, along that ray. With sufficient rays of varying directionality, the entire object can be quantified with respect to its spatially distributed attenuation coefficient. The Hounsfield units (also called CT numbers) are traditionally scaled such that -1000 is dry air and water is zero [CITE].

@@

The reconstruction populates the CT mesh with CT numers, also known as Hounsfield units. These values are related to the attenuation coefficient of the material represented by the voxel. Traditionally, a CT number of zero corresponds to the attenuation of water while -1000 corresponds to dry air [CITE] though some variations do exist \citep{ref:plessisf} \citep{ref:sawc}.

@@

\section{Discrete Ordinates}\label{sec:discordlit}
The dsicrete ordinates method dates back to [CITE] but remains one of the most prominent solution modalities for radiation transport in use today. A comprehensive review of discrete ordinate methods is given by \citet{ref:lewise}. Additional references include [CITES].

@@

Discrete ordinate methods are almost always done on a Cartesian grid, though alternative derivations on general geometry do exist~\citep{ref:dehart}. Extension to unstructured tetrahedral meshes was done by ~\citet{ref:wareingt}.

>>>>

\section{CT Dose Estimation}
As discussed in Chapter 1, the dose a patient receives from both diagnostic CT procedures and radiation therapy is of concern to the medical community. However, dose quantification is not currently patient specific. Measuring the dose in a patient directly is impossible, intead the air kerma (measured in Gy), which measures the x-ray beam intensity, and can be measured directly with ionization chambers~\citep{ef:wolbarsta}. As the x-ray beam passes through the patient, it deposits energy. The energy deposition per unit mass is the absorbed dose (measured in Gy) which is then weighted by the radiation type to give the equivalent dose (measured in Sv). The equivalent dose quantifies the biological detriment to the patient from the procedure. The effective dose (measured in Sv) accounts for the radiosensitivity of each organ and is the most meaningful measure of risk to the patient. Any two procedures that result in the same effective dose to the patient carry the same acute and long-term risks. Any procedure that gives an effective dose to a patient has the same risk as any procedure that would give the same whole body dose.

@@

Monte Carlo codes such as TOPAS~\citep{ref:perlj}, Geant4~\citep{ref:agostinellis}, and MCNP6~\citep{ref:mcnp6} are the current gold standard in computational dosimetry~\citep{ref:jiax}. This work compares results to those obtained from MCNP6. MCNP6 is a Monte Carlo code developed for general purpose particle transport and is well validated. MCNP6 was selected for comparison because it is so well validated and the input files can be easily generated procedurally. Codes whose input such as Geant4 do not lend themselves easily to procedural code generation are difficult to benchmark precisely against for arbitrary computational phantoms.

@@

The method of characteristics solves the characteristic form of the Boltzmann transport equation which is defined along a single direction (called the characteristic). Along that direction, the 3-dimensional gradient operator found in the full Boltzmann equation (see Sec.~\ref{sec:lbe}) becomes a 1-dimensional derivitive. This reduction gives rise to an analytical solution along the characteristic~\citep{ref:askewj}. Sufficient characteristic solutions solved simulateously gives the solution over the entire problem domain. Currently, though, MOC has not been extended to full 3D, instead, hybrid methods such as the NEM-$S_N$ technique employed by DeCART have been used. DeCART uses 2D MOC to solve planar slices of reactor transport problems and links the slices using diffusion~\citep{ref:hursinm}. Another MOC implementation is the TRANSMED code which was used to compute external beam therapy dose profiles accurately~\citep{ref:williamsm}. Method of characteristic solutions have been extended to the time dependent domain by \citet{ref:hoffmana}.

@@

Fundamentally, all reconstructions algorithms are based on a thin parallel beam of x-rays rotating axially about a patient to produce a sinogram. The inverse radon transform backprojects each row of the sinogram back to physical space. Filtering each row in Fourier space and then compositing all layers together recreates the image~\citep{ref:mersereaur}. This methodology has been extended to fan beams~\citep{ref:bessong} and cone beams~\citep{ref:turbellh}. Besides the filtered backprojection (FBP) method, iterative reconstruction techniques can also be applied to greatly improve the image reconstruction quality~\citep{ref:pontanaf}.

@@

Along any particular ray, monoenergetic particles will attenuate through a homogenous media according to the Beer-Lambert law given in Eq.~\ref{eq:beer_lambert}~\citep{ref:lamarshj} resulting in a small fraction of the source particles reaching the detector. This phenomena leads to an image of the attenuating media but also results in the detector receiving information about the attenuation coefficient, $\mu$, along that ray. With sufficient rays of varying directionality, the entire object can be quantified with respect to its spatially distributed attenuation coefficient.

@@

The reconstruction populates the CT mesh with CT numers, also known as Hounsfield units. These values are related to the attenuation coefficient of the material represented by the voxel. Traditionally, a CT number of zero corresponds to the attenuation of water while -1000 corresponds to dry air though some variations do exist \citep{ref:plessisf,ref:sawc}.

@@

\section{Discrete Ordinates}\label{sec:discordlit}
The dsicrete ordinates method dates back to~\citet{ref:chandrasekahar} who used it for radiation transport in atmospheres, yet it remains one of the most prominent solution modalities for radiation transport in use today. A comprehensive review of discrete ordinate methods is given by \citet{ref:lewise}. Additional historical references include~\citet{ref:carlsonb}~\citet{ref:lanthropk}.

@@

Discrete ordinate methods are almost always done on a Cartesian grid, though alternative derivations on general geometry do exist~\citep{ref:dehartm}. Extension to unstructured tetrahedral meshes was done by ~\citet{ref:wareingt}.

### 2017-06-12 docprep/chapconc.tex
Updates

\section{First conclusion}

@@

Anisotropy cannot be ignored.

@@

@@

@@

NJOY or AMPX.

\subsection{Temporal Extension}
Use 4D CT to do temporal stuff as well as spatial stuff.

@@

\subsection{Extension to Therapy Beams}
High energy will be more anisotropic. Will need spherical harmonics.

\subsection{Organ Identification}
Currently, DOCTORS cannot automatically identify specific organs, thus it is only able to compute the equivalent dose via dose deposition.

>>>>

\section{Accuracy}

@@

The collided flux suffers from the isotropic approximation made to simplify the code.

@@

\section{GPU Speedup}

The GPU acceleration algorithm was found to speed the DOCTORS code up by a factor of ~40x.

@@

\subsection{Anisotropy Treatment}
A more sophisticated anisotropy treatment would be appropriate since the collided flux was found to have issues regarding its behavior.

@@

INSERT SECTION ABOUT NJOY or AMPX.

\subsection{Temporal Extension}
An advantage of the raytracer is that it is very fast. Therefore, it can characterize many beams and integrate them temporally easily. This would allow DOCTORS to model more complex beam shapes and scan protocols accurately.

@@

\subsection{Extension to Therapy Beams}
DOCTORS can likely be extended to high energy therapeutic beams for clinical treatment. However, higher energy photons will scatter more anisotropicly. This will require spherical harmonics and high order $P_l$ expansion tables in the cross section data.

\subsection{Organ Identification}
Currently, DOCTORS cannot automatically identify specific organs, thus it is only able to compute the equivalent dose via dose deposition. If specific organs could be identified, tissue specific weighting factors could be applied resulting in the effective dose to each organ which would be of greater clinical significance. However, such identification currently requires additional input about the scan protocol and extensive knowledge about the human anatomy not currently integrated into DOCTORS.

### 2017-06-12 docprep/chapimpl.tex
Updates

@@

The data is stored in Big Endian format which must be converted to Little Endian for most Intel and AMD processors.  The endianess rearrangement is shown in Fig.~\ref{fig:ampxbytes2}. Each record is one of 12 unique types; each type of record is formatted and interpreted differently. For example, Type 1 contains general information about the data file such as the number of nuclides, number of energy groups, and a brief description. Type 2 records contains a list of floating-point numbers representing the energy group boundaries. Figure~\ref{fig:ampxbytes1} shows a Type 1 record. In the case of the header bytes given in Fig.~\ref{fig:ampxbytes1} and~\ref{fig:ampxbytes2}, the bytes correspond to the integer 440 which is the length in bytes of the record (not including the header or footer).

Each byte of data is sequentially read, reordered, and converted to an apprpriately typed variable. Table~\ref{tab:reorder} shows the converstion for the record given in Fig.~\ref{fig:ampxbytes1}.

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=3.75in]{figs/ampxbytes1}
  \end{center}
  \caption{An example record parsed. The header and footer are identical and equal to the number of bytes in the record.}
\label{fig:ampxbytes1}
\end{figure}

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=2.75in]{figs/ampxbytes2}
  \end{center}
  \caption{The byte reordering from Big Endian to Little Endian. Individual bits within a byte are not rearranged, but the ordering of the four bytes withing a 32-bit word is reversed.}
\label{fig:ampxbytes2}
\end{figure}

\begin{table}[ht]
\caption{Byte Reordering}
\centering 
\begin{tabular}{l | c | c | c | l}
  \hline \hline   
  Word  & Big Endian & Little Endian & Interpreted & Notes\\ [0.5ex] % inserts table 
  \hline
  0   & B8 01 00 00 & 00 00 01 B8 & 440    & Header                    \\
  1   & 8B 69 00 00 & 00 00 69 8B & 27019  & ID                        \\
  2   & A4 01 00 00 & 00 00 01 A4 & 420    & Number of nuclides        \\
  ... &      ---    &      ---    &    --- & ---                       \\
  11  & 70 75 6F 43 & 43 6F 75 70 & "Coup" & First word of the title   \\
  12  & 20 64 65 6C & 6C 65 64 20 & "led " & Second word of the title  \\
  ... &     ---     &    ---      &  ---   & ---                       \\
  440 & 20 20 20 20 & 20 20 20 20 & "    " & 4 spaces ending the title \\
  441 & B8 01 00 00 & 00 00 01 B8 & 440    & Footer                    \\ 
  [1ex]      % [1ex] adds vertical space
  \hline
\end{tabular}
\label{table:reorder}
\end{table}

@@

\begin{listing}
\begin{minted}[frame=lines,linenos]{c++}
# Given magic
KKK = magic % 1000
JJJ = (magic % 1000000 - KKK) /1000
III = (magic - JJJ - KKK) / 1000000

@@

Once the data is parsed, weighted combinations of elemental data is used to create material cross sections. Cross section data for photons always uses the naturally ocurring since photo-atomic reactions are not sensitive to the nuclear differences between isotopes. The compositions of N materials are assumed to be given as weight fractions, $w_i$ subject to
\begin{equation}
sum_{i = 1}^N w_i = 1
\end{equation}
and is converted to an atom fraction, $a_i$:
\begin{equation}
a_i = \frac{w_i}{M m_i}
\end{equation}
where
\begin{equation}
M = \sum_{i = 1}^N \frac{w_i}{m_i}
\end{equation}
and $m_i$ is the element's atomic weight.

@@

\begin{listing}
\begin{minted}[frame=lines,linenos]{c++}
class MainWindow : public QWindow
{
	// Constructor
	MainWindow(QObject *parent);

@@

public slot:
	void doSomethingLong();
}

@@

	// When a button named button1 which was created in the Qt5 creator interface is clicked, the clicked() signal is automatically emitted which executes the doSomethingLong() function
	MainWindow.connect(ui->button1, clicked(), this, doSomethingLong())
}
\end{minted}
\caption{A long function causes the user interface to block.}\label{lst:sync1}
\end{listing}

@@

The code in Listing~\ref{lst:sync1} is updated to use the Qt signal/slot mechanism.

\begin{listing}
\begin{minted}[frame=lines,linenos]{c++}
class MainWindow : public QWindow
{
	// Constructor
	MainWindow(QObject *parent);

public slot:
	void doSomethingLong();
}

	// When a button named button1 which was created in the Qt5 creator interface is clicked, the clicked() signal is automatically emitted which executes the doSomethingLong() function
	MainWindow.connect(ui->button1, clicked(), this, doSomethingLong())
}
\end{minted}
\caption{A long function causes the user interface to block.}\label{lst:sync1}
\end{listing}

@@

\section{CUDA}\label{sec:cuda}
CUDA code is compoiled with the Nvidia complier nvcc. Qt uses the gcc compiler and its MOC generator for meta code. In order to connect CUDA code to the Qt MOC, the CUDA code is compiled by nvcc to produce a .o file. Qt then compiles all other files into corresponding.o files. The linker than automactically picks up all of the .o files gneerated by nvcc. The final result is an executable that has a Qt generarted user interface that can communicat with an Nvidia graphics card through the CUDA language.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/subsweep_cube1}
        \caption{Subsweep 0 ($S=0$)}
        \label{fig:subsweep_cube1}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/subsweep_cube2}
        \caption{Subsweep 1 ($S=1$)}
        \label{fig:subsweep_cube2}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/subsweep_cube3}
        \caption{Subsweep 6 ($S=6$)}
        \label{fig:subsweep_cube3}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/subsweep_cube4}
        \caption{Subsweep 6 ($S=6$) with labels}
        \label{fig:subsweep_cube4}
    \end{subfigure}
    \caption{The progression of subsweeps throughout a sweep. Each subsweep must complete before those after it. Each voxel within a subsweep can be solved in parallel with all others in its subsweep.}\label{fig:subsweep_cube}
\end{figure}

>>>>

INSERT NOTE ABOUT CODE LISTING FORMATTING

@@

The data is stored in Big Endian format which must be converted to Little Endian for most Intel and AMD processors.  The endianess rearrangement is shown in Fig.~\ref{fig:ampxbytes2}. Each record is one of 12 unique types; each type of record is formatted and interpreted differently. For example, Type 1 contains general information about the data file such as the number of nuclides, number of energy groups, and a brief description. Type 2 records contains a list of floating-point numbers representing the energy group boundaries. Figure~\ref{fig:ampxbytes1} shows a Type 1 record. In the case of the header bytes given in Fig.~\ref{fig:ampxbytes1} and~\ref{fig:ampxbytes2}, the bytes correspond to the integer 440 which is the length in bytes of the record (not including the header or footer). Each byte of data is sequentially read, reordered, and converted to an apprpriately typed variable. Table~\ref{tab:reorder} shows the converstion for the record given in Fig.~\ref{fig:ampxbytes1}.

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=4.75in]{figs/ampxbytes1}
  \end{center}
  \caption{An example record parsed. The header and footer are identical and equal to the number of bytes in the record.}
\label{fig:ampxbytes1}
\end{figure}

\begin{figure}[tb]
  \begin{center}
   \includegraphics[width=4.75in]{figs/ampxbytes2}
  \end{center}
  \caption{The byte reordering from Big Endian to Little Endian. Individual bits within a byte are not rearranged, but the ordering of the four bytes withing a 32-bit word is reversed.}
\label{fig:ampxbytes2}
\end{figure}

\begin{table}[ht]
\caption{Byte Reordering}
\centering 
\begin{tabular}{l | c | c | c | l}
  \hline \hline   
  Word  & Big Endian & Little Endian & Interpreted & Notes\\ [0.5ex] % inserts table 
  \hline
  0   & B8 01 00 00 & 00 00 01 B8 & 440    & Header                    \\
  1   & 8B 69 00 00 & 00 00 69 8B & 27019  & ID                        \\
  2   & A4 01 00 00 & 00 00 01 A4 & 420    & Number of nuclides        \\
  ... &      ---    &      ---    &    --- & ---                       \\
  11  & 70 75 6F 43 & 43 6F 75 70 & "Coup" & First four \texttt{char} of the title   \\
  12  & 20 64 65 6C & 6C 65 64 20 & "led " & Second four \texttt{char} of the title  \\
  ... &     ---     &    ---      &  ---   & ---                       \\
  110 & 20 20 20 20 & 20 20 20 20 & "    " & 4 spaces ending the title \\
  111 & B8 01 00 00 & 00 00 01 B8 & 440    & Footer                    \\ 
  [1ex]      % [1ex] adds vertical space
  \hline
\end{tabular}
\label{tab:reorder}
\end{table}

@@

\begin{listing}
\begin{minted}[frame=lines,linenos]{c++}
magic = READ_NEXT_BINARY_INT()
KKK = magic % 1000
JJJ = (magic % 1000000 - KKK) /1000
III = (magic - JJJ - KKK) / 1000000

@@

Once the data is parsed, weighted combinations of elemental data is used to create material cross sections. Cross section data for photons always uses the naturally ocurring since photo-atomic reactions are not sensitive to the nuclear differences between isotopes. The compositions of N materials are assumed to be given as weight fractions, $w_i$ subject to
\begin{equation}
\sum_{i = 1}^N w_i = 1
\end{equation}
and is converted to an atom fraction, $a_i$:
\begin{equation}
a_i = \frac{w_i}{M m_i}
\end{equation}
where
\begin{equation}
M = \sum_{i = 1}^N \frac{w_i}{m_i}
\end{equation}
and $m_i$ is the element's atomic weight.

@@

\begin{listing}
\begin{minted}[frame=lines,linenos]{c++}
class MainWindow : public QMainWindow
{
	// Constructor
	MainWindow(QObject *parent);

@@

protected slots:
	void doSomethingLong();
}

@@

	// When a button named button1 which was created in the Qt5
	creator interface is clicked, the clicked() signal is 
	automatically emitted which executes the doSomethingLong()
	function
	connect(ui->button1, clicked(), this, 
		doSomethingLong());
}
\end{minted}
\caption{A long function causes the user interface to block.}\label{lst:sync1}
\end{listing}

@@

The code in Listing~\ref{lst:sync1} is updated to use the Qt signal/slot mechanism whose code is given in Listing~\ref{lst:async1}.

\begin{listing}
\begin{minted}[frame=lines,linenos]{c++}
class MainWindow : public QWindow
{
	// Member variables
	QThread workerThread;
	Worker *worker;

	// Constructor
	MainWindow(QObject *parent);

protected slots:
	handleResult();
}

MainWindow::MainWindow(QObject *parent)
{
	// Initializations
	worker = new Worker;

	worker.moveToThread(&workerThread);

	// Set up the thread connections
	connect(&workerThread, finished(), worker, deleteLater());
	connect(this, begin(), worker, doSomethingLong());
	connect(worker, done(), this, handleResult());
}

class Worker : public QObject
{
private signals:
	void done();

public slots:
	void soSomethingLong();
}

Worker::doSomethingLong()
{
	// Do stuff...
	emit done();
}

\end{minted}
\caption{Signals and slots enable a long function to be called without blocking the user interface.}\label{lst:async1}
\end{listing}

@@

\section{CUDA}\label{sec:cuda}
CUDA code is compoiled with the Nvidia complier nvcc. Qt5 uses the gcc compiler and its MOC generator for meta code. In order to connect CUDA code to the Qt MOC, the CUDA code is compiled by nvcc to produce a .o file. Qt5 then compiles all other files into corresponding.o files. The linker than automactically picks up all of the .o files gneerated by nvcc. The final result is an executable that has a Qt5 generarted user interface that can communicat with an Nvidia graphics card through the CUDA language.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/subsweep_cube1}
        \caption{}
        \label{fig:subsweep_cube1}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/subsweep_cube2}
        \caption{}
        \label{fig:subsweep_cube2}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/subsweep_cube3}
        \caption{}
        \label{fig:subsweep_cube3}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/subsweep_cube4}
        \caption{) with labels}
        \label{fig:subsweep_cube4}
    \end{subfigure}
    \caption{The progression of subsweeps throughout a sweep. Each subsweep must complete before those after it. Each voxel within a subsweep can be solved in parallel with all others in its subsweep. (a) Subsweep 0 ($S=0$) (b) Subsweep 1 ($S=1$) (c) Subsweep 6 ($S=6$) (d)Subsweep 6 ($S=6$) with labels.}\label{fig:subsweep_cube}
\end{figure}

### 2017-06-12 docprep/chapintro.tex
Updates

Since its introduction in 1973 by \citet{ref:hounsfieldg} computed tomography (CT) has become pervasive in medical diagnostics as improved algorithms and techniques give doctors access to higher quality information. Increased information results in faster and more accurate diagnosis. However, the exponentially increasing usage of CT and dose patients receive from it has raised concerns of potential long term risks~\citep{ref:brennerd} \citep{ref:einsteina1} \citep{ref:abramsh} \citep{ref:einsteina2} \citep{ref:mccolloughc} \citep{ref:yul}. These concerns are exemplified by the push for low dose CT.

INSERT MORE LOW DOSE CT STUFF
A study by \citet{ref:kovalchiks} found that using a low-dose screening method as opposed to CT radiography reduced lung cancer mortality in high risk patients by 20\%.

@@

Another, similar, application is dose estimation of patients receiving radiation therapy. Often, before the procedure, a time dependent, 4D CT scan of the patient is taken so that radiologists can account for breathing patterns during administration of the treatment [CITE]. With further development, this methodology may enable real time dose computation as the treatment is administered. This would be greatly beneficial to both patients and the doctors administering the procedure.

>>>>

Since its introduction in 1973 by \citet{ref:hounsfieldg} computed tomography (CT) has become pervasive in medical diagnostics as improved algorithms and techniques give doctors access to higher quality information. Increased information results in faster and more accurate diagnosis. However, the exponentially increasing usage of CT and dose patients receive from it has raised concerns of potential long term risks~\citep{ref:brennerd,ref:einsteina1,ref:abramsh,ref:einsteina2,ref:mccolloughc,ref:yul}. These concerns are exemplified by the push for low dose CT.

%INSERT MORE LOW DOSE CT STUFF
%A study by \citet{ref:kovalchiks} found that using a low-dose screening method as opposed to CT radiography reduced lung cancer mortality in high risk patients by 20\%.

@@

Another, similar, application is dose estimation of patients receiving radiation therapy. Often, before the procedure, a time dependent, 4D CT scan of the patient is taken so that radiologists can account for breathing patterns during administration of the treatment~\citep{ref:pant}. With further development, this methodology may enable real time dose computation as the treatment is administered. This would be greatly beneficial to both patients and the doctors administering the procedure.
